The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-27 exp-resurgence.tex
Show thimbles over both 1 and -1

    \includegraphics[width=6.5cm]{figures/ray_1.png}

@@

    \includegraphics[width=6.5cm]{figures/thimble-n5_1.png}
    \caption{The ray $\Gamma^{\pi/6}_{\zeta, 1}$ on the position domain, and its preimage in the $u$ plane.}

@@

Choose a ciritcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\Lambda_a^\theta$:

@@

\subsection{Airy--Lucas}\label{example_AL}
The Airy-Lucas equation is
\begin{equation}\label{eqn:airy-lucas}
\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
\end{equation}
with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
where $\Lambda^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$. %%(see Figure \ref{fig:thimble_n_5}).
By definition, $\Lambda^\theta_j$ is a preimage of the ray $\Gamma^\theta_{\mp 1}$ under the function $-T_n(u)$. The ray starts at the critical value $-1$ when $j$ is even, and $1$ when $j$ is odd.
\begin{center}
\includegraphics[scale=0.3]{figures/thimble-n5.png} \\[1em]
{\small Integration contour $\Lambda^{(j)}$ for the Airy--Lucas function with $n=5$. The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=\textcolor{magenta}{???}$. The light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
\end{center}
\begin{figure}[ht]
    \centering
   \includegraphics[scale=0.3]{figures/thimble-n5.png}
    \caption{Integration contour $\Lambda^\theta_j$ for the Airy--Lucas function with $n=5$. The dark blue contours correspond to the preimage of the ray \textcolor{magenta}{$1+e^{i\theta}\infty$ [convert to $\Gamma$]} and \textcolor{orange}{$\theta=???$}. While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$. \textcolor{orange}{[Preferred version, with ``Figure'' label]}}
    \label{fig:thimble_n_5}
\end{figure}

>>>>

    \includegraphics[width=6.5cm]{figures/rays.png}

@@

    \includegraphics[width=6.5cm]{figures/thimbles-n5.png}
    \caption{The rays $\Gamma^{\pi/8}_{\zeta, \pm 1}$ on the position domain, and their preimages in the $u$ plane.}

@@

Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\Lambda_a^\theta$:

@@

\subsection{Airy--Lucas}\label{example_AL}
The Airy-Lucas equation is
\begin{equation}\label{eqn:airy-lucas}
\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
\end{equation}
with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
where $\Lambda^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$. %%(see Figure \ref{fig:thimble_n_5}).
By definition, $\Lambda^\theta_j$ is a preimage of the ray $\Gamma^\theta_{\mp 1}$ under the function $-T_n(u)$. The ray starts at the critical value $-1$ when $j$ is even, and $1$ when $j$ is odd.
\begin{center}
\includegraphics[width=10cm]{figures/thimbles-n5.png} \\[1em]
{\small Integration contour $\Lambda^{(j)}$ for the Airy--Lucas function with $n=5$. The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=\textcolor{magenta}{???}$. The light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
\end{center}
\begin{figure}[ht]
    \centering
   \includegraphics[width=10cm]{figures/thimbles-n5.png}
    \caption{Integration contours $\Lambda^\theta_j$ for the Airy--Lucas functions with $n=5$. The dark and light thimbles are the preimages of the rays $\Gamma^{\pi/8}_{\zeta, 1}$ and $\Gamma^{\pi/8}_{\zeta, -1}$, respectively. \textcolor{orange}{[Preferred version, with ``Figure'' label]}}
    \label{fig:thimble_n_5}
\end{figure}
